\documentclass[10pt, letterpaper]{article}

% Packages for layout and formatting
\usepackage[utf8]{inputenc}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[ someborder]{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{geometry}

% Page geometry setup
\geometry{
    left=0.6in,
    right=0.6in,
    top=0.6in,
    bottom=0.6in
}

% Color definitions
\definecolor{primaryColor}{RGB}{44, 52, 93} % Sleek dark blue
\definecolor{textColor}{RGB}{30, 30, 30}   % Soft black for readability

\urlstyle{same}
\hypersetup{
    colorlinks=true,
    linkcolor=primaryColor,
    urlcolor=primaryColor
}

% Section heading formatting
\titleformat{\section}{
    \large\bfseries\color{primaryColor}
}{}{0em}{}[\color{primaryColor}\titlerule \vspace{-4pt}]

% Custom list environment for bullet points
\newlist{cvitems}{itemize}{1}
\setlist[cvitems]{
    label=\textbullet,
    leftmargin=1.5em,
    rightmargin=0em,
    topsep=2pt,
    itemsep=3pt,
    parsep=0pt
}

\begin{document}
\color{textColor}

%=========================================
% HEADER SECTION
%=========================================
\begin{center}
    {\LARGE \bfseries \color{primaryColor} PRATIK SHINGALA} \\ \vspace{4pt}
    Data Analyst (in training) | Operations \& Insights \\ \vspace{6pt}
    \small 
    Berlin, Germany \ $\cdot$ \ 
    +49 176 93192 102 \ $\cdot$ \ 
    \href{mailto:Pratikshingala03@gmail.com}{Pratikshingala03@gmail.com}
\end{center}

%=========================================
% PROFILE
%=========================================
\section*{PROFILE}
\vspace{2pt}
Analytical and detail-oriented data analyst in training with hands-on experience optimising inventory operations through real-time tracking and sales-trend analysis. Currently pursuing a B.Sc. in Computer Science and applying strong communication, teamwork, and multitasking skills to deliver actionable insights in fast-paced environments.

%=========================================
% PROFESSIONAL EXPERIENCE
%=========================================
\section*{PROFESSIONAL EXPERIENCE}

\vspace{4pt}
\textbf{Junior Operations Manager} \hfill Nov 2023 -- Present \\
\textit{Burgermeister Berlin} \hfill Berlin, Germany
\begin{cvitems}
    \item Oversee employee records, payroll budgeting, contract administration, and meeting coordination.
    \item Designed and implemented a new staff-scheduling system that reduced shift conflicts and improved workforce utilisation.
    \item Manage vendor relationships and track departmental budgets to control costs and support growth initiatives.
\end{cvitems}

\vspace{6pt}
\textbf{Junior Data Analyst} \hfill Oct 2022 -- Oct 2023 \\
\textit{Amazon} \hfill Munich, Germany
\begin{cvitems}
    \item Analysed sales trends and customer feedback to identify opportunities and recommend strategies to increase revenue.
    \item Monitored real-time inventory across multiple warehouses to enable proactive supply-chain decisions and reduce stockouts.
    \item Prepared actionable reports and visualisations to inform management reviews and operational adjustments.
    \item Collaborated with cross-functional teams on performance management and employee relations.
\end{cvitems}

\vspace{6pt}
\textbf{Working Student -- AI-Powered Developer Tools} \hfill Oct 2020 -- Oct 2022 \\
\textit{Amazon} \hfill Surat, India
\begin{cvitems}
    \item Developed and maintained AI-powered developer tools that integrated large language models into the software development life cycle to support code quality and developer decision-making.
    \item Built features to detect developer knowledge gaps, suggest code improvements, and automate routine checks to increase developer productivity.
    \item Collaborated with engineers and product managers to design experiments, iterate on models, and measure impact.
\end{cvitems}

%=========================================
% EDUCATION
%=========================================
\section*{EDUCATION}

\vspace{4pt}
\textbf{B.Sc. Computer Science} \hfill Oct 2023 -- Present \\
\textit{GISMA University of Applied Sciences} \hfill Germany

%=========================================
% SKILLS
%=========================================
\section*{SKILLS}

\vspace{4pt}
\textbf{Data \& Programming:} Python, MySQL, Cloud Computing \\
\textbf{Analytics:} Sales-trend analysis, Real-time inventory tracking, Reporting \& visualisation, Social-media analysis \\
\textbf{Tools \& Platforms:} Google Workspace, Jira, CMS management, SEO optimisation \\
\textbf{Professional:} Planning \& organising, Communication, Problem solving, Teamwork

%=========================================
% COURSES & CERTIFICATIONS
%=========================================
\section*{COURSES \& CERTIFICATIONS}

\vspace{4pt}
\textbf{Google Cloud Fundamentals: Core Infrastructure} \hfill Jan -- Jun 2025 \\
\textit{Coursera}

\vspace{4pt}
\textbf{Developing a Google SRE Culture} \hfill Jul -- Dec 2025 \\
\textit{Coursera}

%=========================================
% EXTRACURRICULAR
%=========================================
\section*{EXTRACURRICULAR}

\vspace{4pt}
\textbf{Advent of Cyber 2025} \hfill Nov 2025 \\
\textit{TryHackMe} \hfill Berlin, Germany
\begin{cvitems}
    \item Completed hands-on modules and CTF-style challenges across web exploitation, forensics, network security, and cryptography.
    \item Applied Linux and scripting tools to investigate vulnerabilities and automate repetitive analysis tasks.
    \item Documented step-by-step write-ups and remediation recommendations, and collaborated on team-based attack/defense challenges.
\end{cvitems}

%=========================================
% LANGUAGES
%=========================================
\section*{LANGUAGES}
\vspace{4pt}
German, English, Gujarati, Hindi

\end{document}